Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2019-12-07 lloveras_2020.tex
sigue la milonga

*Paso 1: obtencion de FBE
*Paso 2: obtencion LDEM
\begin{equation}\label{fbeldem}
\FBE_i^{(k)}  = \int\,\textrm{d}T\,\LDEM_i(T)\,{\TRF}^{(k)}(T), \ \ \ {k=1,...,K}
\end{equation}

>>>>

*Paso 1: obtencion de FBE\\
*Paso 2: obtencion LDEM
\begin{equation}\label{fbeldem}
\FBE_i^{(k)}  = \int\,\textrm{d}T\,\LDEM_i(T)\,{\TRF}^{(k)}(T), \ \ \ {k=1,...,K}
\end{equation}

\textcolor{red}{
Due to unresolved coronal dynamics, tomographic reconstructions exhibit negative values of the reconstructed FBE, or zero when the solution is constrained to positive values \citep{frazin_2000,frazin_2009}. {These non-reconstructed voxels are indicated in black in the Carrington maps of reconstructed FBE}.
}
